Multiprocessing air palletization and tour planning for simultaneous pickup and delivery

### 2022-11-10 latex/comp_or.tex
Experimentation initiated

\title{Parallel air palletization and tour planning for simultaneous pickup and delivery}

@@

These challenging benchmark instances are made publicly available. We also created a parallel computing heuristic that quickly finds good solutions for a wide range of problem sizes, an essential contribution as it was the unique method that managed to solve all testing scenarios.

@@

Below, we present five implementations for $SolveNode$: the first using a MIP solver, and four with developed heuristics: {\it Ant Colony Optimization}\/ (ACO), {\it Parallel Ant Colony Optimization}\/ (ACO-p),  and {\it Shims},  and {\it Parallel Shims (Shims-p)}.

@@

		\multirow{2}{*}{\textbf{Shims}}   & $f$              & 6.47        & 3.90        & 3.30         & 3.25         & 3.13         & 6.03        &   \\ 
		                                  &{\bf run-time (s)}& <1          & 1           & 2            & 18           & 46           & 138         &   \\ %206s
		\midrule[.1pt]

		\multirow{2}{*}{\textbf{Shims-p}} & $f$              & 6.47        & 3.90        & 3.30         & 3.25         & 3.13         & 6.03        &   \\ 
		                                  &{\bf run-time (s)}& 3           & 4           & 3            & 12           & 64           & 213         &   \\ %299s
		\midrule[.1pt]

		\multirow{2}{*}{\textbf{ACO}}     & $f$              & 6.19        & 3.63        & 3.21         &        &       &      &   \\ 
                                          &{\bf run-time (s)}& 5           & 239         & 572          &        &       &      &   \\ 
        \midrule[.1pt]

        \multirow{2}{*}{\textbf{ACO-p}}   & $f$              & 6.04        & 4.23        & 3.61         &         &       &       &   \\ 
                                          &{\bf run-time (s)}& 3           & 72          & 196          &         &       &       &   \\

>>>>

\title{Multiprocessing air palletization and tour planning for simultaneous pickup and delivery}

@@

These challenging benchmark instances are made publicly available. We also created a multiprocessing computing heuristic that quickly finds good solutions for a wide range of problem sizes, an essential contribution as it was the unique method that managed to solve all testing scenarios.

@@

Below, we present five implementations for $SolveNode$: the first using a MIP solver, and four with developed heuristics: {\it Ant Colony Optimization}\/ (ACO), {\it Multiprocessed Ant Colony Optimization}\/ (ACO-p),  and {\it Shims},  and {\it Multiprocessed Shims (Shims-p)}.

@@

		\multirow{2}{*}{\textbf{Shims}}   & $f$              & 6.24        & 4.07        &          &          &          &         &   \\ 
		                                  &{\bf run-time (s)}& <1          & 1           &             &            &            &          &   \\ %206s
		\midrule[.1pt]

		\multirow{2}{*}{\textbf{Shims-p}} & $f$              & 6.59        & 3.95        &          &          &          &         &   \\ 
		                                  &{\bf run-time (s)}& 2           & 12          &             &            &            &          &   \\ %299s
		\midrule[.1pt]

		\multirow{2}{*}{\textbf{ACO}}     & $f$              & 6.05        &         &          &        &       &      &   \\ 
                                          &{\bf run-time (s)}& 26          &          &           &        &       &      &   \\ 
        \midrule[.1pt]

        \multirow{2}{*}{\textbf{ACO-p}}   & $f$              & 5.90        &         &          &         &       &       &   \\ 
                                          &{\bf run-time (s)}& 12          &           &           &         &       &       &   \\
